Reducing Acceptance Marks in Emerson-Lei Automata by QBF Solving

### 2023-06-05 paper/main.tex
fix of the spell check

\begin{figure}[p]
  \centering
  \input{quantile.tex}
  \bigskip\bigskip
  \input{quantile-random.tex}
  \bigskip
  \caption{Performance of \telatko on individual automata of each automata set.
    Automata sets constructed from formulas from literature are in the upper graph,
    automata sets constructed from random formulas are in the lower graph.
    Each line shows the time ($y$ axis) needed by \telatko to process the
    $x$-Th automaton of the set, where automata in the set are ordered by
    their processing time.
    % The $x$ axis represents the number of automata from each automata
    % set that are processed by \telatko in the time shown on the $y$
    % axis.
  }
\label{fig:quantile}\end{figure}

>>>>

\begin{figure}[p]
  \centering
  \input{quantile.tex}
  \bigskip\bigskip
  \input{quantile-random.tex}
  \bigskip
  \caption{Performance of \telatko on individual automata of each automata set.
    Automata sets constructed from formulas from literature are in the upper graph,
    automata sets constructed from random formulas are in the lower graph.
    Each line shows the time ($y$ axis) needed by \telatko to process the
    $x^\textrm{th}$ automaton of the set, where automata in the set are ordered by
    their processing time.
    % The $x$ axis represents the number of automata from each automata
    % set that are processed by \telatko in the time shown on the $y$
    % axis.
  }
\label{fig:quantile}\end{figure}
